A robust and memory-efficient transition state search method for complex energy landscapes

### 2022-08-22 manuscript.tex
Updated size and caption of fig 3

\subsection{Comparison with chain-of-states methods}
\begin{figure*}[tb]
  \includegraphics[width=\linewidth]{testsystems.pdf}
  \caption{\label{fig:testsystems}
    Comparisons between BITSS, DNEB, and the string method in the distance from the transition state as a function of the number of calculations of the energy gradient.
    Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
    The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
    The string method and DNEB are repeated with a differing number of images, as listed in the legend in (c).
  }
\end{figure*}

>>>>

\subsection{Comparison with chain-of-states methods}
\begin{figure}[tb]
  \includegraphics{testsystems.pdf}
  \caption{\label{fig:testsystems}
    The three systems used for comparison with chain-of-states methods.
    These are: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
    The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
  }
\end{figure}
